On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
Cosmetic fixes
[AMZAE] Remove TODO notes

TODO: three ''romantic'' pictures in a row.

@@

\end{itemize}
TODO: specify the irrational distance:

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search an intuition of the authors.
The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo

>>>>

@@

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search and intuition of the authors.
The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo
